
\begin{thebibliography}{99}

\bibitem{comon94} Comon, P. (1994). 
``Independent Component Analysis: a new concept?'', 
Signal Processing, 36(3):287–314

\bibitem{bellSejnowski95} Bell, A.J. and Sejnowski, T.J. (1995).,
``An information maximization approach to blind separation and blind deconvolution'', 
Neural Computation, 7, 1129-1159

\bibitem{pearlmutterParra}Pearlmutter, B. A. and Parra, L. C.(1996),
``A Context-Sensitive Generalization of ICA''. 

\bibitem{hyvarinen2001}Hyvarinen A (2001),
``Independent Component Analysis'',
Neural Computing Surveys, Neural Computing Surveys, vol 2.

\bibitem{bach} Bach, F.R. and Jordan, M.I. (2004),
``Blind One-Microphone Speech Separation: A Spectral Learning
  Approach''.

\bibitem{fastICA}Hyvärinen, A. (1999),
``Fast and Robust Fixed-Point Algorithms for Independent Component
  Analysis''. 
IEEE Transactions on Neural Networks 10(3):626-634, 1999.

\bibitem{roweisOneMic}Roweis, Sam T.(2001).
``One Microphone Source Separation"
Neural Information Processing Systems 13 (NIPS'00).
pp. 793-799
  
\bibitem{davies2007}Davies, M.E. and James, C.J. (2007).
``Source separation using single channel ICA'',
Signal Process., vol. 87, no. 8, pp. 1819–1832, 2007.

\bibitem{cardoso98}Cardoso, J. L.(1998),
``Multidimensional Independent Component Analysis'',
Proceedings of ICASSP 1998.

\bibitem{mijovic2010} Mijovic, B. De Vos, M.,  Gligorijevic, I.,
  Taelman, J. and Van Huffel, S. (2010),
``Source Separation From Single-Channel Recordings by Combining
  Empirical-Mode Decomposition and Independent Component Analysis'',
IEEE Transactions on Biomedical Engineering, vol. 57, no. 9, September 2010

\bibitem{VargaHMMDecomp}Varga, A. P., and R. K. Moore. 
``Hidden Markov model decomposition of speech and noise"
Acoustics, Speech, and Signal Processing, 1990. ICASSP-90., 1990 International Conference on. IEEE, 1990.

\bibitem{pearson1901}{Pearson, K. (1901). ``On Lines and Planes of Closest Fit to Systems of Points in Space". Philosophical Magazine 2 (6): 559–572.}

\bibitem{Pham}{Pham, D. T. and Garat, P. (1992) ``Blind Separation of Mixture of Independent Sources Through a Maximum Likelihood Approach'', Proc. EUSPICO, pp. 771-774.}

\bibitem{norvig_russel}{Russell, S. and Norvig, P. (2010). ``Artificial
    Intelligence: A Modern Approach''.}

\bibitem{roweisMaxVQ}{Roweis, Sam T.
``Factorial models and refiltering for speech separation and denoising"
 In Proc. EuroSpeech, Geneva (Vol. 7, pp. 1009-1012).}

\bibitem{ESL}{Hastie, T., Tibshirani, R. and Friedman, J. 
``The Elements of Statistical Learning: Data Mining, Inference and Prediction (Second Edition)
2009}


\end{thebibliography}





